Refinements for open automata

### 2022-06-03 2021-Refinement/paper/refinementarticle.tex
work session
beter holes in identical transition condition

%
%\begin{definition}[Deadlock reduction]\label{def:dpwd}\\
%Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
%A relation on OA configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following\footnote{Note that variables of $T_1$ are existentially quantified in the proposition.}:
%\begin{multline*}
% \forall \mpar{s_1, s_2} \in S_1 \times S_2,
% \\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
%\end{multline*}
%\end{definition}

@@

>>>>

\begin{definition}[Preservation along identical transitions]\label{def:preservation} \\
Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) between  \(\OAg[1]\) and \(\OAg[2]\)
  is preserved along identical transitions if  it satisfies the following:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
\implies \\
\exists
\OTx{1}{a}{3}{3}\in \fOT{s_1}. \alpha_1=\alpha_{1 a} \land g_{1 a} \land \bigwedge_\subbox{j \in J'_3 \cap J'_2} \beta_{2j} = \beta_{3j}\land
 R\mpar{s'_{1 a}, s'_2}\psubst{\psi_{1 a} \uplus \psi_2}\\
\end{multline*}
\end{definition}
\TODO{check les actions des trous -- Je pense que c est mieux maintenant}
%
%\begin{definition}[Deadlock reduction]\label{def:dpwd}\\
%Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
%A relation on OA configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following\footnote{Note that variables of $T_1$ are existentially quantified in the proposition.}:
%\begin{multline*}
% \forall \mpar{s_1, s_2} \in S_1 \times S_2,
% \\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
%\end{multline*}
%\end{definition}

@@

\TODO{add a notion of composable at hole i:
An OA is composable at hole k if it is partially deterministic relatively to actions of hole k
}

\begin{multline*}
\forall s_1\in S,\, \forall \OTx{1}{a}{1}{1}, \OTx{1}{b}{2}{2} \in \fOT{s_1}.\\
\neg\left(\alpha_{1 a} = \alpha_{1 b}\land s'_{1 a}\neq s'_{1 b}\land g_{1 a}\land g_{1 b} \land\beta_{1 k} \neq \beta_{2 k}\right)
\end{multline*}

An composable automaton cannot transform external non-determinism of the sub-automaton into internal non-determinism.
